### 2022-04-29 greta/sn_mcmc.Rmd
refreshed sn
fix typo in metadata

```{r}
set.seed(4242)
train_reps <- 100
train_t_max <- 250
test_t_max <- 250
test_reps <- 100
simulate <- simulate_sn
```

@@

```{r}
scores <-
  rep_scores(combined, "N") |> 
  mutate(scenario="stochastic", 
         model="MCMC", 
         reps = train_reps)

>>>>

```{r}
set.seed(4242)
train_reps <- 1
train_t_max <- 250
test_t_max <- 250
test_reps <- 100
simulate <- simulate_sn
```

@@

```{r}
scores <-
  rep_scores(combined, "N") |> 
  mutate(scenario="saddle_node", 
         model="MCMC", 
         reps = train_reps)
